Paper Visualization

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
new tables and reorg

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "aids_descriptive_statistics_table_relevancy_filtered.html")

@@

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic.html")
gtsave(gt_table, output_file_path)
```

@@

# Save the plot to a PNG file with increased size
ggsave(file.path(output_directory, "images and tables", "co-occurrence_network.png"), 
       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
```

@@

output_file_path <- file.path(output_directory, "images and tables", "influential_authors_descriptive_statistics.html")

@@

# Combine the sentiment statistics into one table
combined_sentiment_stats <- bind_rows(
  aids_sentiment_stats,  # AIDS-related discussions
  usenet_sentiment_stats,  # Entire Usenet dataset
  influential_authors_sentiment_stats  # Influential authors
) %>%
  select(Dataset, everything())  # Ensure 'Dataset' column is the first column

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "sentiment_score_descriptive_statistics_combined.html")

@@

# Save the plot to a PNG file
output_file_path <- file.path(output_directory, "images and tables", "time_series_sentiment_plot.png")
ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
```

@@

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic (Influential Authors).html")
gtsave(gt_table, output_file_path)
```

@@

output_file_path <- file.path(output_directory, "images and tables", "topic_matches_table.html")

@@

ggsave(file.path(output_directory, "images and tables", "topic_influence_comparison.png"), 
       width = 10, height = 6, dpi = 300)
```

@@

# Save the plot with a higher DPI for better clarity
output_file_path <- file.path(output_directory, "images and tables", "topic_prevalence_line_plot.png")
ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
```

>>>>

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_aids_relevancy_filtered.html")

@@

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(all_authors).html")
gtsave(gt_table, output_file_path)
```

@@

# Save the plot to a PNG file with increased size
ggsave(file.path(output_directory, "images and tables", "plot_co-occurrence_network.png"), 
       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
```

@@

output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")

@@

# Combine the sentiment statistics into one table
combined_sentiment_stats <- bind_rows(
  usenet_sentiment_stats,  # Entire Usenet dataset
  aids_sentiment_stats,  # AIDS-related discussions
  influential_authors_sentiment_stats  # Influential authors
) %>%
  select(Dataset, everything())  # Ensure 'Dataset' column is the first column

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_sentiment_scores_combined.html")

@@

# Save the plot to a PNG file
output_file_path <- file.path(output_directory, "images and tables", "plot_time_series_sentiment_line_graph.png")
ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
```

@@

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(influential_authors).html")
gtsave(gt_table, output_file_path)
```

@@

output_file_path <- file.path(output_directory, "images and tables", "table_topic_matches.html")

@@

ggsave(file.path(output_directory, "images and tables", "plot_topic_influence_comparison_bar_graph.png"), 
       width = 10, height = 6, dpi = 300)
```

@@

# Save the plot with a higher DPI for better clarity
output_file_path <- file.path(output_directory, "images and tables", "plot_topic_prevalence_line_graph.png")
ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
```
